General Physics Formula

### 2016-10-25 Complex Geometry - index/part 1/Notations.tex
1.New physics GRE prep. 2. Learn to organize tex into small subfiles.

% The entire content of this work (including the source code
% for TeX files and the generated PDF documents) by 
% Hongxiang Chen (nicknamed we.taper, or just Taper) is
% licensed under a 
% Creative Commons Attribution-NonCommercial-ShareAlike 4.0 
% International License (Link to the complete license text:
% http://creativecommons.org/licenses/by-nc-sa/4.0/).
\documentclass{article}

\usepackage{float}  % For H in figures
\usepackage{amsmath} % For math
\usepackage{amssymb}
\usepackage{mathrsfs}
\numberwithin{equation}{subsection} % have the enumeration go to the subsection level.
									% See:https://en.wikibooks.org/wiki/LaTeX/Advanced_Mathematics
\usepackage{graphicx}   % need for figures
\usepackage{cite} % need for bibligraphy.
\usepackage[unicode]{hyperref}  % make every cite a link
\usepackage{CJKutf8} % For Chinese characters
\usepackage{fancyref} % For easy adding figure,equation etc in reference. Use \fref or \Fref instead of \ref
\usepackage{braket} %http://tex.stackexchange.com/questions/214728/braket-notation-in-latex

% Following is for theorems etc environments
% http://tex.stackexchange.com/questions/45817/theorem-definition-lemma-problem-numbering && https://en.wikibooks.org/wiki/LaTeX/Theorems
\usepackage{amsthm}
\newtheorem{thm}{Theorem}
\newtheorem{lemma}{Lemma}

\usepackage{xcolor} %For colourful math:http://tex.stackexchange.com/questions/21598/how-to-color-math-symbols

\title{Complex Geometry - Index of Notations and ideas}
\date{\today}
\author{Taper}

\begin{document}

\maketitle
\tableofcontents

\begin{abstract}
Obviously.

\end{abstract}

\section{Book}
	\subsection{1. Local Theory}
		\subsubsection{1.1 Holomorphic Functions of Several Variables}
		\label{sec:1.1_book}
		\textbf{Note}: the content covered by this seciton is geared for accompanying my personal notes of lecture 1.

@@

		\textcolor{blue}{1}: 
		\textcolor{blue}{1}:
		\textcolor{blue}{1}:
		\textcolor{blue}{1}:
		\textcolor{blue}{1}: 
		\textcolor{blue}{1}:
		\textcolor{blue}{1}:
		\textcolor{blue}{1}:

	\subsection{2.Complex Manifolds}

		\subsubsection{2.2 Holomorphic Vector Bundles}

@@

	\subsection{Lecture 17 Hermitian Vector Bundle (20160510)}
	pp.1,3:
	\begin{itemize}
		\item Hermitian Vector Bundle. pp.1
		\item Antilinear map. pp.3.
		\item Hermitian Inner Product on $\mathcal{A}^{p,q}(X,E)$. pp.4
		\item $\bar{*}_E$ Hodge Operator on Hermitian vector bundle. pp.5.
		\item $\bar{\partial}_E^*$
	\end{itemize}
	pp. 8:
	\begin{itemize}
		\item Kadaira-Serre Duality.
	\end{itemize}

	\subsection{Lecture 18 Connection (20160516)}
	\begin{itemize}
		\item $\bigtriangledown$: connection. pp.1.
		\item Trivial connections. pp.2
		\item $\mathcal{A}^1(M,End(E)):=\Gamma(M,\Lambda^1 M\otimes End(E))$. pp.3. Also, one may find how elements in this sheaf act on $\mathcal{A}^0(M)$ on pp.173, inside proof of proposition 4.2.3.
		\item $s\in \mathcal{A}^0(E)$ is Parrallel/flat/constant $\Leftrightarrow \Delta(s) = 0$. pp.4.
		\item $\Delta = d+A$. pp.4.
		\item $\Delta$ be compatible with hermitian structure on $E$. pp.5.
		\item $\Delta$ be compatible with holomorphic vector bundle. pp.6.
		\item $A=\bar{H}^{-1} \partial H$. Chern connection. pp.6.
	\end{itemize}

	\subsection{Lecture 19 Holomorphic Connection \& Curvature(20160517)}
	\begin{itemize}
		\item Holomorphic Connecction. pp.1.
		\item $At(E)$: Atiyah class of $E$. pp.2.
		\item $\Delta^k$. pp.4.
		\item $F_\Delta$: curvature associated with $\Delta$. pp.5.
		\item $F_\Delta = dA + A\wedge A$: Cartan structure equation. pp.6.
		\item First Chern class of complex line bundle.
	\end{itemize}

	\subsection{Lecture 20 Divisors \& (Holomorphic) Line Bundles (20160524)}
	\begin{itemize}
		\item Analytic Subvariety. pp.1.
		\item Regular/Smooth Point. pp.1.
		\item Singular Point. pp.2.
		\item Irreducible analytic subvariety. pp.2.
		\item $dim(Y)$: dimension of analytic subvariety. pp.2. Also pp.4.
		\item Affine algebraic varieties. pp.3.
		\item Projective algebraic varieties. pp.3.
		\item Hypersurface. pp.4.
		\item Divisor, $Div(X)$:=group of all divisors. pp.5.
		\item Effective divisor. pp.6.
		\item $Ord_Y(f)$: order of function. pp.6. Also pp.8.
		\item Meromorphic function on complex mnfd.
		\item $(f)$: divisor given by a global meromorphic function.
		\item Principal divisor. pp.8.
	\end{itemize}

	\subsection{Lecture 21 Divisors \& (Holomorphic) Line Bundles  (20160530)}
	\begin{itemize}
		\item $H^0(X,K^*_X/\mathcal{O}^*_X) \cong Div(X)$. pp.1.
		\item $Pic(X)$: Picard group, all holomorphic line bundles. pp.3.
		\item $Pic(X) \cong \check{H}^1(X,\mathcal{O}^*_X)$. pp.3.
		\item $\mathcal{O}(D)$: line bundle given by divisor $D$. pp.5.
		\item Linear equivalent of divisors.
		\item $*$: used only in this section to denoted the map:
		$$\left( Div(X)/Pic(X) \right) \hookrightarrow Pic(X)$$
		pp.6.
		\item $Z(s)$: divisor constructed from nonzero section $s\in H^0(X,L)$ for a line bundle $L$.
	\end{itemize}

	\subsection{Lecture 22 Divisors \& (Holomorphic) Line Bundles (20160606)}
	\begin{itemize}
		\item Base point of a line bundle. pp.4.
		\item $Bs(L)$:= set of all base points of line bundle $L$. pp.4.
		\item $\mathcal{O}(1), \mathcal{O}(k)$. pp.6.
	\end{itemize}

\begin{thebibliography}{1}

	\bibitem{blog} Complex Geometry

\end{thebibliography}
\section{License}
The entire content of this work (including the source code
for TeX files and the generated PDF documents) by 
Hongxiang Chen (nicknamed we.taper, or just Taper) is
licensed under a 
\href{http://creativecommons.org/licenses/by-nc-sa/4.0/}{Creative 
Commons Attribution-NonCommercial-ShareAlike 4.0 International 
License}. Permissions beyond the scope of this 
license may be available at \url{mailto:we.taper[at]gmail[dot]com}.
\end{document}

>>>>

\chapter{Book}
\section{1. Local Theory}
    \subsection{1.1 Holomorphic Functions of Several Variables}
    \label{sec:1.1_book}
    \textbf{Note}: the content covered by this seciton is geared for accompanying my personal notes of lecture 1.

@@

    \textcolor{blue}{germ of set}: (\textbf{pp.18})

    \textcolor{blue}{$Z(f)$}: germ of zero set of $f$. (\textbf{pp.18})

    \textcolor{blue}{analytic germ}: $Z(f_1,\cdots,f_k)$. (\textbf{pp.18})

    \textcolor{blue}{analytic subset}: locally are zero sets. (\textbf{pp.18})

    \textcolor{blue}{$I(X)$}: the set of all $f\in
    \mathcal{O}_{\mathbb{C}^n,0}$ with $X\subset Z(f)$. (\textbf{pp.18})
    % TODO bookmark
    \subsection{1.2 Complex and Hermitian Structures}
    \textcolor{blue}{almost complex structure, $I$}: $I^2=-\text{id}$.
    (\textbf{pp.25})

    \textcolor{blue}{$V^{1,0}$ and $V^{0,1}$}: the $\pm i$ eigenspaces 
    of $I$.
    (\textbf{pp.25})

    \textcolor{blue}{$\bigwedge^{p,q} V$}:=
    $\bigwedge^p V^{1,0}\oplus_{\mathbb{C}}\bigwedge^q V^{0,1}$.
    (\textbf{pp.27})

    \textcolor{blue}{$\prod^k,\prod^{p,q}$}: natural projections.
    (\textbf{pp.28})

    \textcolor{blue}{$\mathbf{I}$}:=$\sum_{p,q}i^{p-q}\cdot\prod^{q,p}$.
    (\textbf{pp.28})

    \textcolor{blue}{compatible}:an almost complex structure $I$ is
    compatible with the scalar product $<,>$, if $<I(v),I(w)>=<v,w>$.
    (\textbf{pp.28})

    \textcolor{blue}{Conformal equivalence}(between scalar product):
    (\textbf{pp.29})

    \textcolor{blue}{fundamental form, $\omega$}:=$<I\text{( )},()>.$
    (\textbf{pp.29})
    $$\omega=\frac{i}{2}\sum_i z^i\wedge\bar{z}^i=\sum_i x^i\wedge y^i.$$
    \quad(Local calculation could be found on \textbf{pp.31})

    \textcolor{blue}{hermitian form $(,)$}:=$<,>-i\cdot\omega$.
    (\textbf{pp.30})

    \textcolor{blue}{Lefschetz operator $L$}:
        $\bigwedge^* V^*_{\mathbb{C}}\to
    \wedge^* V_{\mathbb{C}}^*$, given by $\alpha\to\omega\wedge\alpha$.
    (\textbf{pp.31})

    \textcolor{blue}{Hodge star $*$-operator}: $\alpha\wedge *\beta=
        \langle\alpha,\beta\rangle \cdot \text{vol}$.
    (\textbf{pp.33})

    \textcolor{blue}{dual Lefschetz operator $\Lambda$}:
        $\langle\Lambda\alpha,\beta\rangle =\langle\alpha,L\beta\rangle$,
        degree $-2$, bidegree $(-1,-1)$, $\Lambda=*^{-1}\circ L\circ *$.
    (\textbf{pp.33 to 34})

    \textcolor{blue}{Counting operator $H$}:
        $H=\sum_{k=0}^{2n}(k-n)\cdot\prod^k$, 
        where $\text{dim}_{\mathbb{R}}=2n$.
    (\textbf{pp.34})

    \textcolor{blue}{commutator [A,B]}:$=A\circ B-B\circ A$.
    (\textbf{pp.34})

\paragraph{Commutators}
$$[H,L]=2L,\text{ } [H,\Lambda]=-2\Lambda,\text{ } [L,\Lambda]=H.$$
(\textbf{pp.34})

$$[L^i,\Lambda](\alpha)= i(k-n+i-1)L^{i-1}(\alpha),\text{for all}
    \alpha\in\bigwedge^k V^*$$
(\textbf{pp.35})

    \textcolor{blue}{primitive element} in $\bigwedge^kV^*$:
        $\alpha$ is primitive if and only if $\Lambda\alpha=0$.
    (\textbf{pp.36})

    \textcolor{blue}{$P^k$} $\subset\bigwedge^kV^*$: is the subspace
    of all primitive elements.
    (\textbf{pp.36})

    \textcolor{blue}{Hodge-Riemann pairing $Q$}:
    $$\bigwedge^kV^*\times\bigwedge^kV^*\to \mathbb{R}\text{, }
     (\alpha,\beta)\mapsto (-1)^{k(k-1)}{2}\alpha\wedge\beta\wedge w^{n-k}$$

    Note: here we identify $\bigwedge^{2n}V^*$ with $\mathbb{R}$ 
    by the volumn form $\text{vol}$. Also the $\mathbb{C}$-linear 
    extension of this is still denoted $Q$.

\section{2.Complex Manifolds}

    \subsection{2.1 Complex and Hermitian Structures}
    \textcolor{blue}{almost complex structure}: (\textbf{pp.25})
	\subsection{2.2 Holomorphic Vector Bundles}

@@

\section{Lecture 17 Hermitian Vector Bundle (20160510)}
pp.1,3:
\begin{itemize}
    \item Hermitian Vector Bundle. pp.1
    \item Antilinear map. pp.3.
    \item Hermitian Inner Product on $\mathcal{A}^{p,q}(X,E)$. pp.4
    \item $\bar{*}_E$ Hodge Operator on Hermitian vector bundle. pp.5.
    \item $\bar{\partial}_E^*$
\end{itemize}
pp. 8:
\begin{itemize}
    \item Kadaira-Serre Duality.
\end{itemize}

\section{Lecture 18 Connection (20160516)}
\begin{itemize}
    \item $\bigtriangledown$: connection. pp.1.
    \item Trivial connections. pp.2
    \item $\mathcal{A}^1(M,End(E)):=\Gamma(M,\Lambda^1 M\otimes End(E))$. pp.3. Also, one may find how elements in this sheaf act on $\mathcal{A}^0(M)$ on pp.173, inside proof of proposition 4.2.3.
    \item $s\in \mathcal{A}^0(E)$ is Parrallel/flat/constant $\Leftrightarrow \Delta(s) = 0$. pp.4.
    \item $\Delta = d+A$. pp.4.
    \item $\Delta$ be compatible with hermitian structure on $E$. pp.5.
    \item $\Delta$ be compatible with holomorphic vector bundle. pp.6.
    \item $A=\bar{H}^{-1} \partial H$. Chern connection. pp.6.
\end{itemize}

\section{Lecture 19 Holomorphic Connection \& Curvature(20160517)}
\begin{itemize}
    \item Holomorphic Connecction. pp.1.
    \item $At(E)$: Atiyah class of $E$. pp.2.
    \item $\Delta^k$. pp.4.
    \item $F_\Delta$: curvature associated with $\Delta$. pp.5.
    \item $F_\Delta = dA + A\wedge A$: Cartan structure equation. pp.6.
    \item First Chern class of complex line bundle.
\end{itemize}

\section{Lecture 20 Divisors \& (Holomorphic) Line Bundles (20160524)}
\begin{itemize}
    \item Analytic Subvariety. pp.1.
    \item Regular/Smooth Point. pp.1.
    \item Singular Point. pp.2.
    \item Irreducible analytic subvariety. pp.2.
    \item $dim(Y)$: dimension of analytic subvariety. pp.2. Also pp.4.
    \item Affine algebraic varieties. pp.3.
    \item Projective algebraic varieties. pp.3.
    \item Hypersurface. pp.4.
    \item Divisor, $Div(X)$:=group of all divisors. pp.5.
    \item Effective divisor. pp.6.
    \item $Ord_Y(f)$: order of function. pp.6. Also pp.8.
    \item Meromorphic function on complex mnfd.
    \item $(f)$: divisor given by a global meromorphic function.
    \item Principal divisor. pp.8.
\end{itemize}

\section{Lecture 21 Divisors \& (Holomorphic) Line Bundles  (20160530)}
\begin{itemize}
    \item $H^0(X,K^*_X/\mathcal{O}^*_X) \cong Div(X)$. pp.1.
    \item $Pic(X)$: Picard group, all holomorphic line bundles. pp.3.
    \item $Pic(X) \cong \check{H}^1(X,\mathcal{O}^*_X)$. pp.3.
    \item $\mathcal{O}(D)$: line bundle given by divisor $D$. pp.5.
    \item Linear equivalent of divisors.
    \item $*$: used only in this section to denoted the map:
    $$\left( Div(X)/Pic(X) \right) \hookrightarrow Pic(X)$$
    pp.6.
    \item $Z(s)$: divisor constructed from nonzero section $s\in H^0(X,L)$ for a line bundle $L$.
\end{itemize}

\section{Lecture 22 Divisors \& (Holomorphic) Line Bundles (20160606)}
\begin{itemize}
    \item Base point of a line bundle. pp.4.
    \item $Bs(L)$:= set of all base points of line bundle $L$. pp.4.
    \item $\mathcal{O}(1), \mathcal{O}(k)$. pp.6.
\end{itemize}

### 2016-10-25 GRE Physics Prep/General Physics Formula.tex
1.New physics GRE prep. 2. Learn to organize tex into small subfiles.

\paragraph{Waves} (\textbf{pp.436 ch16 of \cite{book}})
\begin{align}
    & y(x,t) = y_m \sin(kx-\omega t) \\
    & k = \frac{2\pi}{\lambda} \\
    & f = \frac{\omega}{2\pi} = \frac{1}{T} \\
    & v = \frac{\omega}{k} = \frac{\lambda}{T} = \lambda f
\end{align}
\textbf{String}
\begin{align}
    & v = \frac{\tau}{\mu} \\
    & P_\text{avg} = \frac{1}{2}\mu v \omega^2 y_m^2
\end{align}
\textbf{Resonance}
\begin{align}
    n \lambda = 2L
\end{align}
\paragraph{Longitudinal Wave} (\textbf{pp.466 ch17 of \cite{book}})
\begin{align}
    & v = \sqrt{\frac{B}{\rho}} \\
    & s = s_m \cos(kx-\omega t) \\
    & \Delta p = \Delta p_m sin(kx-\omega r) \\
    & \Delta p_m = (v\rho \omega) s_m
\end{align}
\textbf{Sound Intensity}
\begin{align}
    & I = \frac{P}{A} \\
    & I = \frac{1}{2}\rho v \omega^2 s_m^2 \\
    & I = \frac{P_s}{4\pi r^2} \\
\end{align}
\textbf{Standing Wave Patterns in Pipes}
\begin{align}
    & f = \frac{v}{\lambda} = \frac{nv}{2L}\text{, $n=1,2,3,\cdots$} \\
    & f = \frac{v}{\lambda} = \frac{nv}{4L}\text{, $n=1,3,5,\cdots$}
\end{align}
\begin{figure}[H]
    \centering
    \includegraphics[width=0.8\linewidth]{pics/{ch17.sound_wave}.png}
\end{figure}
\textbf{Beat}
\begin{align}
    f_\text{beat} = f_1 - f_2
\end{align}
\textbf{The Doppler Effect}
\begin{align}
    f' = f \frac{ v \pm v_D}{ v\pm v_s}
\end{align}
The signs are chosen such that $f'$ tends to be \textit{greater} for
motion toward and \textit{less} for motion away.
\textbf{Shock wave}
\begin{align}
    \sin{\theta} = \frac{v}{v_s}\text{ , $v_s\geq v$}
\end{align}

@@

\paragraph{Electric field} (\textbf{pp.596 ch22 of \cite{book}})
\begin{align}
    & E = \frac{1}{4\pi \varepsilon_0} \frac{q}{r^2} \\
    & E = \frac{1}{2\pi \varepsilon_0} \frac{p}{z^3} \\
    & U = - \vec{p}\cdot \vec{E} 
\end{align}

@@

\paragraph{Magnetic -> Electricity} (\textbf{pp.781 ch29 of
\cite{book}})

>>>>

\paragraph{Waves} (\textbf{pp.436 ch16 of \cite{book}})
\begin{align}
    & y(x,t) = y_m \sin(kx-\omega t) \\
    & k = \frac{2\pi}{\lambda} \\
    & f = \frac{\omega}{2\pi} = \frac{1}{T} \\
    & v = \frac{\omega}{k} = \frac{\lambda}{T} = \lambda f
\end{align}

\begin{figure}[H]
    \centering
    \includegraphics[width=0.8\linewidth]{pics/{wave-and-reflection}.PNG}
    \caption{wave and Reflection}
\end{figure}
$(a)$ A pulse incident from the right is reflected at the left end of
the string, which is tied to a wall. Note that the reflected pulse is
inverted from the incident pulse. $(b)$ Here the left end of the string
is tied to a ring that can slide without friction up and down the rod.
Now the pulse is not inverted by the reflection

\textbf{String}
\begin{align}
    & v = \frac{\tau}{\mu} \\
    & P_\text{avg} = \frac{1}{2}\mu v \omega^2 y_m^2
\end{align}
\textbf{Resonance}
\begin{align}
    n \lambda = 2L
\end{align}
\paragraph{Longitudinal Wave} (\textbf{pp.466 ch17 of \cite{book}})
\begin{align}
    & v = \sqrt{\frac{B}{\rho}} \\
    & s = s_m \cos(kx-\omega t) \\
    & \Delta p = \Delta p_m sin(kx-\omega r) \\
    & \Delta p_m = (v\rho \omega) s_m
\end{align}
\textbf{Sound Intensity}
\begin{align}
    & I = \frac{P}{A} \\
    & I = \frac{1}{2}\rho v \omega^2 s_m^2 \\
    & I = \frac{P_s}{4\pi r^2} \\
\end{align}
\textbf{Standing Wave Patterns in Pipes}
\begin{align}
    & f = \frac{v}{\lambda} = \frac{nv}{2L}\text{, $n=1,2,3,\cdots$} \\
    & f = \frac{v}{\lambda} = \frac{nv}{4L}\text{, $n=1,3,5,\cdots$}
\end{align}
\begin{figure}[H]
    \centering
    \includegraphics[width=0.8\linewidth]{pics/{ch17.sound_wave}.png}
\end{figure}
\textbf{Beat}
\begin{align}
    f_\text{beat} = f_1 - f_2
\end{align}
\textbf{The Doppler Effect}
\begin{align}
    f' = f \frac{ v \pm v_D}{ v\pm v_s}
\end{align}
The signs are chosen such that $f'$ tends to be \textit{greater} for
motion toward and \textit{less} for motion away.
\textbf{Shock wave}
\begin{align}
    \sin{\theta} = \frac{v}{v_s}\text{ , $v_s\geq v$}
\end{align}

@@

\paragraph{Lorentz Force Law}
\begin{equation}
    \vb{F} = q\left(\vb{E} +\vb{v}\cross\vb{B}\right)
\end{equation}
\paragraph{Electric field} (\textbf{pp.596 ch22 of \cite{book}})
\begin{align}
    & E = \frac{1}{4\pi \varepsilon_0} \frac{q}{r^2} \\
    & E = \frac{1}{2\pi \varepsilon_0} \frac{p}{z^3} \\
    & U = - \vec{p}\cdot \vec{E} 
\end{align}

@@

\paragraph{Magnetic $\to$ Electricity} (\textbf{pp.781 ch29 of
\cite{book}})
